Key Provisioning for the Internet of Things via Light

### 2015-10-13 paper/paper.tex
change references style to 'acm'
some things

@@

\begin{abstract}
The rise of the Internet of Things (IoT) is associated with an enormous increase in every-day devices that get connected to the Internet.
In order to avoid privacy issues and security threats those devices have to communicate securely using state-of-the-art encryption techniques.
However, these techniques often rely on predistributed keying material.
Secure distribution of these initial keys \textit{before} securing techniques are operational remains a major problem.

We propose a secure method for IoT-device initialization by transmitting initial keying material via light.
The transmission can be executed using an off-the-shelf smartphone and doesn't require any technical expertise.
\end{abstract}

@@

The Internet of Things (IoT) is becoming more and more of a reality every day.
It consists of small devices (called \textit{motes}), which are connected to the public Internet, \cite{atzori2010internet}.
They work together, allowing monitoring and controlling of several kinds of real-world systems.
An example are motes collecting information about parking lot occupancy, allowing car drivers to find free spaces using their smartphones\footnote{see http://www.streetline.com/}.

In the last decades, the rise of embedded systems changed daily lives.
However, these systems often had limited networking capabilities or at least used their own, proprietary and thus unaccessible network technology.
Because of the huge variety of valuable possibilities, the impact of embedded systems will be advanced even further within the IoT.

However, this comes at a price: by being accessible from the Internet, the attack surface of such systems is much larger than that of traditional embedded systems.
New security measures had to be developed and implemented to react to this.
For example, \textit{Adaptive Key Establishment Scheme (AKES)} provides adaptable security measures for being used with the IEEE~802.15.4 network stack, which is commonly used by IoT devices, \cite{krentz15akes}.
Nevertheless, one problem remains: IoT setups usually consist of many nodes which all need to be initialized with keying material and parameters.
This is a major problem, because typical motes lack input/output devices which are securely usable without configured networking.

% figure is inserted here to be shown on page 1
\begin{figure}
	\centering
	\includegraphics[scale=.4]{images/overview.png}
	\caption{Transmission of keying material with light: \textbf{a)} enter and encode key and parameters on smartphone, \textbf{b)} transmit them via light to the mote, \textbf{c)} persist key and parameters, \textbf{d)} communicate securely via the public Internet }
	\label{fig:overview}
\end{figure}

One possibility is to plug a wire to each and every node in order to initialize it.
However, there are two downsides: First, a typical IoT setup consists of too many devices for plugging to be a feasible solution. Second, in most installations, attackers may have physical access to motes, so jacks on the mote (e.g. JTAG) are a dangerous security threat.

Another approach is to pre-initialize the keys in the factory.
This would mean that either there is a small set of assigned keys, which would lead to possible brute-force attacks; or each mote gets an individual key, which requires a secure transmission and attribution of keys to motes\footnote{This would also increase cost of motes, but they need to be as cheap as possible in order to be affordable in great numbers.}.
Anyway, pre-initialization requires somebody other than the user/installer to know the keys, which diminishes security.

This paper proposes an alternative way, which is transmitting initial keying material via light.
It is mainly targeted on private users without technical background and should provide them with a simple though secure process for initializing.

@@

% Bibliography
\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{paper}

>>>>

% \bibliographystyle{abbrv}

@@

\begin{abstract}
The rise of the Internet of Things (IoT) is associated with an enormous increase in every-day devices that get connected to the Internet.
In order to avoid privacy issues and security threats those devices have to communicate securely using state-of-the-art encryption techniques.
However, these techniques often rely on predistributed key material.
The secure and user-friendly provisioning of the initial key meterial \textit{before} securing techniques are operational remains a major problem.

We propose a secure method for provisioning keys for IoT-devices via light.
The transmission can be executed using an off-the-shelf smartphone and does not require any technical expertise.
\end{abstract}

@@

The Internet of Things (IoT) is becoming more and more of a reality every day.
It consists of small devices (henceforth called \textit{motes}), which are connected to the public Internet, \cite{atzori2010internet}.
They work together, allowing monitoring and controlling of several kinds of real-world systems.
An example are motes collecting information about parking lot occupancy, allowing car drivers to find free spaces using their smartphones\footnote{see http://www.streetline.com/}.

However, by being accessible from the Internet, the attack surface of such systems is much larger than that of traditional embedded systems.
New security measures were developed and implemented to react to this.
For example, \textit{Adaptive Key Establishment Scheme (AKES)} provides adaptable security measures for being used with the IEEE~802.15.4 network stack, which is commonly used by IoT devices, \cite{krentz15akes}.
Nevertheless, one problem remains: IoT setups usually consist of many nodes which all need to be provisioned with keying material and parameters.
This is a major problem, because typical motes lack input/output devices that are securely usable without configured networking.

\begin{figure}
	\centering
	\includegraphics[scale=.4]{images/overview.png}
	\caption{Transmission of keying material with light: \textbf{a)} enter and encode key and parameters on smartphone, \textbf{b)} transmit them via light to the mote, \textbf{c)} persist key and parameters, \textbf{d)} communicate securely via the public Internet }
	\label{fig:overview}
\end{figure}

One method is to plug a wire to each and every node in order to initialize it.
However, there are two downsides: First, a typical IoT setup consists of too many devices for plugging to be a feasible solution. Second, in most installations, attackers may have physical access to motes, so jacks on the mote (e.g. JTAG) are a dangerous security threat.

Another approach is to pre-install the keys in the factory.
This would mean that either there is a small set of assigned keys, which would lead to possible brute-force attacks; or each mote gets an individual key, which requires a secure transmission and attribution of keys to motes\footnote{This would also increase cost of motes, but they need to be as cheap as possible in order to be affordable in great numbers.}.
Anyway, pre-initialization requires somebody other than the user/installer to know the keys, which diminishes security.

This paper proposes an alternative method, which is transmitting initial keying material via light.
It is mainly targeted on private users without technical background and should provide them with a simple though secure process for initializing.

@@

% Bibliography
% \bibliographystyle{ACM-Reference-Format-Journals}
\bibliographystyle{abbrv}
\bibliography{paper}
